Tulai

### 2024-10-23 paper/paper.qmd
map edited

library(ggmap) # devtools::install_github("stadiamaps/ggmap")

@@

# map with site names next to the points
map_of_sites <-
  ggmap(map)  +
  geom_point(data = site_locations,
             aes(y = `Longitude DD` ,
                 x = `Latitude DD`),
             colour = "red",
             size = 2) +
  # label points with site name
  geom_text_repel(data = site_locations,
             aes(y = `Longitude DD` ,
                 x = `Latitude DD`,
                      label = Site),
                  size = 2,
                  bg.color = "white",
                  bg.r = 0.15) +
  theme_minimal(base_size = 6) +
  labs(x = "Longitute",
       y = "Latitude") +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank())

@@

worldplot <- 
ggplot(data = world) +
     geom_sf(color = "black", 
             fill = "white",
             linewidth = 0.05) +
    annotate("rect",
           xmin = bbox[3],
           xmax = bbox[1],
           ymin = bbox[2],
           ymax = bbox[4],
           fill = NA,
           colour = "red",
           linewidth = 0.5
  ) +
  theme_void() +
  theme(panel.background = element_rect(fill = "white"))

@@

ggsave(here::here("figures/site-map.png"),
       width = 4.45,
       height = 4.75,
       units = "in")

>>>>

library(ggmap) # devtools::install_github("stadiamaps/ggmap")
library(ggmap)
ggmap::register_stadiamaps(key = "ca45118a-734f-480b-8c3c-8d82e5a361e3")

@@

# map with site names next to the points
map_of_sites <-
  ggmap(map)  +
  geom_point(data = site_locations,
             aes(y = `Longitude DD` ,
                 x = `Latitude DD`),
             colour = "red",
             size = 0.5) +
  # label points with site name
  geom_text_repel(data = site_locations,
             aes(y = `Longitude DD` ,
                 x = `Latitude DD`,
                      label = Site),
                  size = 2,
                  bg.color = "white",
                  bg.r = 0.15) +
  theme_minimal(base_size = 10) +
  labs(x = "Longitute",
       y = "Latitude") +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank())

@@

worldplot <- 
ggplot(data = world) +
     geom_sf(color = "black", 
             fill = "white",
             linewidth = 0.05) +
    annotate("rect",
           xmin = bbox[1],
           xmax = bbox[3],
           ymin = bbox[2],
           ymax = bbox[4],
           fill = NA,
           colour = "red",
           linewidth = 0.5
  ) +
  theme_void() +
  theme(panel.background = element_rect(fill = "white"))

@@

ggsave(here::here("figures/site-map.png"),
       width = 4.45,
       height = 4.75,
       units = "in", 
       dpi = 300
       )
